IRS-aided SWIPT: Joint waveform, active and passive beamforming design

### 2020-09-24 main.tex
:art: Update styles
:pencil: Improve introduction

\begin{section}{Introduction}
	\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
		With the great advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks. Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner. The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.

		The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels. Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup. Information and power beamforming was then considered in multiuser Multi-Input Single-Output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}. Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems. However, \cite{Boshkovska2015} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level, which also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm. From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency. \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current under rate constraints. Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}. The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region. In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications. By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adapted conventional modulation schemes to ensure WPT is only activated at the points with large offset. Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin. It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity. SWIPT was also explored in the network design. \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user. In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted Sum-Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
	\end{subsection}

	\begin{subsection}{Intelligent Reflecting Surface}
		Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal. Compared with the linear increase in Amplify-and-Forward (AF) relay, the received power scales quadratically with the number of reflectors \cite{Wu2019}, since more reflectors boost the power collected by IRS and increase the array gain in its equal gain transmission.

		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage. Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR). The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency-Division Multiplexing (OFDM) systems. \cite{Yang2019} exploited spatial correlation to reduce estimation overhead and design complexity by assuming adjacent elements share a common reflection coefficient. On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}. By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB). Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.

		Most existing papers assume a Frequency-Flat (FF) IRS where all elements reflect different frequencies equally. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is prohibitive since active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics and unable to adjust channel adaptively \cite{Anwar2018}.
	\end{subsection}

	\begin{subsection}{IRS-aided SWIPT}
		The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. Based on linear harvester model and energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints. The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power on the assumption of perfect energy interference cancellation. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated and a single energy stream can satisfy the energy constraints of all ERs. In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms. However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
	\end{subsection}

	\begin{subsection}{Objective and Methodology}
		In this paper, we study an IRS-aided broadband downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g. OFDM) to boost the energy transfer efficiency without introducing additional interference. The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff. Different from previous research, this paper focus on broadband SWIPT and investigates the fundamental impact of harvester nonlinearity on IRS design. We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints. To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) technique. Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations. We demonstrate that dedicated power waveform boosts the energy transmission efficiency, such that TS and PS are preferred for low-rate and high-rate applications respectively. Also, IRS brings a significant channel amplification thus R-E enhancement especially when located near the transmitter/receiver, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
	\end{subsection}
\end{section}

@@

	\begin{figure}
		\centering
		\def\svgwidth{\columnwidth}
		\import{assets/}{system.pdf_tex}
		\caption{An IRS-aided OFDM SWIPT system}
		\label{fi:system}
	\end{figure}

@@

		\begin{figure}
			\begin{minipage}[b]{0.5\linewidth}
				\centering
				\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
					\resizebox{\linewidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_s$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
					}
				}
			\end{minipage}%
			\begin{minipage}[b]{0.5\linewidth}
				\centering
				\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
					\resizebox{\linewidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
					}
				}
			\end{minipage}
			\caption{Rectenna circuits}
		\end{figure}

@@

		When $\boldsymbol{\Phi}^{\star}$ is rank-1, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is obtained by Eigenvalue Decomposition (EVD). Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}. Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}. Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:irs}.
		\begin{algorithm}
			\caption{SCA: IRS Phase Shift}
			\label{al:irs}
			\begin{algorithmic}[1]
				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
				\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
				\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$, $n=-N+1,\dots,N-1$
				\Repeat
					\State $i \gets i + 1$
					\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem \ref{op:irs}
					\State Compute $z^{(i)}$ by \ref{eq:z_irs}
				\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
				\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
				\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
					\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
				\Else
					\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$

					\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
					\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
					\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
				\EndIf
				\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

		\begin{algorithm}

@@

@@

	\begin{subsection}{Alternating Optimization}
		For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm \ref{al:irs} and transmit waveform together with receive splitting ratio by Algorithm \ref{al:waveform} until convergence. The alternating algorithm is summarized in Algorithm \ref{al:alternating}.
		\begin{algorithm}
			\caption{Alternating Algorithm for Problem \ref{op:original}}
			\label{al:alternating}
			\begin{algorithmic}[1]
				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,\sigma_n,\bar{R},Q,\epsilon$
				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
				\Repeat
					\State $i \gets i + 1$
					\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
					\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $n=1,\dots,N$ by \ref{eq:h_n} and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm \ref{al:waveform}
					\State Compute $z^{(i)}$ by \ref{eq:z_irs}
				\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
				\State \textbf{Output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/re_subband.tex}
		\end{adjustbox}
		\caption{Average R-E region versus the number of subbands}
		\label{fi:re_subband}
	\end{figure}

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/waveform_subband.tex}
		\end{adjustbox}
		\caption{Sorted waveform amplitude versus the number of subbands}
		\label{fi:waveform_subband}
	\end{figure}

@@

	\begin{figure}
		\centering
		\begin{adjustbox}{width=\linewidth}
			\input{assets/re_noise.tex}
		\end{adjustbox}
		\caption{Average R-E region and splitting ratio versus the average noise power}
		\label{fi:re_noise}
	\end{figure}

>>>>

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, the main challenge of wireless network has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks. Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power in \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Ng2018}. The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.

			The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels. Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup. Information and power beamforming was then considered in multiuser Multi-Input Single-Output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}. Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, scheduling schemes, and interference management for SWIPT systems. However, \cite{Boshkovska2015} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level. The authors also suggested a curve-fitting based parametric harvester model and proposed an iterative resource allocation algorithm. From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency. \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and performed waveform design accordingly. Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}. The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is employed to enlarge the R-E region. In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications. Modulation and coding schemes for SWIPT are also becoming popular. By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate versus battery overflow/underflow probability. It suggested that WPT should be activated only at constellation points with large offset. Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the optimal information symbols are symmetrically distributed around the origin. It confirmed that the superposed waveform is effective to enlarge R-E region when considering rectifier nonlinearity. SWIPT was also explored in the network design. \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user. SWIPT based on Rate Splitting (RS) technique was also explored in \cite{Mao2019}.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) adapts the wireless channel to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics with no flexibility \cite{Anwar2018}.

			Inspired by the advance of real-time reconfigurable metamaterials in \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage. Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR). The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency-Division Multiplexing (OFDM) systems. \cite{Yang2019} exploited spatial correlation to reduce estimation overhead and design complexity by assuming adjacent elements share a common reflection coefficient. On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}. By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB). Its application to interference cancellation and secure communication are also investigated in \cite{Zhou2020,Cui2019}. Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
		\end{subsection}

		\begin{subsection}{IRS-aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. Assuming harvester model and energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints. The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power on the assumption of perfect energy interference cancellation. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated thus a single energy stream can satisfy the energy constraints of all ERs. In \cite{Pan2019a}, the authors proposed low-complexity BCD algorithms to maximize the Weighted Sum-Rate (WSR) of Information Receivers (IRs) subject to the power constraint at Energy Receivers (ERs). However, most existing IRS-assisted SWIPT papers focused on narrow-band transmission for separated IRs and ERs based on an oversimplified linear harvester model.
		\end{subsection}

		\begin{subsection}{Objective and Methodology}
			In this paper, we study an IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g. OFDM) to boost the energy transfer efficiency without creating additional interference. The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff. Different from previous research, this paper focus on multicarrier SWIPT and investigates the fundamental impact of harvester nonlinearity on IRS design. The R-E region characterization problem is transformed into multiple current maximization problems subject to different rate constraints. To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) technique. Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations. We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR. Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed near the transmitter or the receiver. Finally, the proposed adaptive IRS design outperformed the benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form for narrowband transmission.
		\end{subsection}
	\end{section}

@@

		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided OFDM SWIPT system}
			\label{fi:system}
		\end{figure}

@@

			\begin{figure}[!t]
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
						\resizebox{\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_s$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}%
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
						\resizebox{\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}
				\caption{Rectenna circuits}
			\end{figure}

@@

			When $\boldsymbol{\Phi}^{\star}$ is rank-1, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is obtained by Eigenvalue Decomposition (EVD). Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}. Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}. Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:irs}.
			\begin{figure}[!t]
				\forcealgorithm
				\begin{algorithm}[H]
					\caption{SCA: IRS Phase Shift}
					\label{al:irs}
					\begin{algorithmic}[1]
						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
						\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
						\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$, $n=-N+1,\dots,N-1$
						\Repeat
							\State $i \gets i + 1$
							\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem \ref{op:irs}
							\State Compute $z^{(i)}$ by \ref{eq:z_irs}
						\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
						\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
							\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
						\Else
							\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$

							\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
							\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
							\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
						\EndIf
						\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
						\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
					\end{algorithmic}
				\end{algorithm}
			\end{figure}
		\end{subsection}

@@

			\begin{figure}[!t]
				\begin{algorithm}[H]
					\forcealgorithm

@@

			\end{figure}

@@

		\begin{subsection}{Alternating Optimization}
			For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm \ref{al:irs} and transmit waveform together with receive splitting ratio by Algorithm \ref{al:waveform} until convergence. The alternating algorithm is summarized in Algorithm \ref{al:alternating}.
			\begin{figure}[!t]
				\begin{algorithm}[H]
					\forcealgorithm
					\caption{Alternating Algorithm for Problem \ref{op:original}}
					\label{al:alternating}
					\begin{algorithmic}[1]
						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,\sigma_n,\bar{R},Q,\epsilon$
						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
						\Repeat
							\State $i \gets i + 1$
							\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
							\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $n=1,\dots,N$ by \ref{eq:h_n} and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm \ref{al:waveform}
							\State Compute $z^{(i)}$ by \ref{eq:z_irs}
						\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
						\State \textbf{Output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
					\end{algorithmic}
				\end{algorithm}
			\end{figure}
		\end{subsection}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus the number of subbands}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{Sorted waveform amplitude versus the number of subbands}
			\label{fi:waveform_subband}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus the average noise power}
			\label{fi:re_noise}
		\end{figure}
